Forecasting US Presidential Election Results Using Bayesian Prediction

### 2024-11-04 paper/paper.qmd
Update and rename paper_FV1.qmd to paper.qmd

kable(candidate_results %>% select(answer, probability), 
      format = "markdown", 
      caption = "Top 4 Candidates Results Table")
```
@tbl-table1 show trump is the most likely candidate to win with an average percentage of 35.52.
Vote Percentage Distribution
Finally, we visualize the vote percentage distribution of the top candidates.

>>>>

kable(candidate_results %>% select(answer, probability),
  format = "markdown",
  caption = "Top 4 Candidates Results Table"
)
```
@tbl-table1 show Trump is the most probable outcome (34%), followed by Biden (27%), Harris (20%), and Ballay (19%).
